\textbf{Course: Física Teórica I (CDP7600)} \\[0.2cm] {\Large \textbf{Project}: \hspace{0.2cm} \textit{Fibration building blocks of information-processing networks} }

### 2019-11-06 Manuscript/main.tex
going

% faltou o preprocessing.

@@

In the algorithm \ref{alg:split} above, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output. Besides its list of nodes, a block $X$ should have another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$. This way, a node $w$ belonging to the block splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm \ref{alg:split}. In cases where the type of connections are non-trivial, i. e., there is more than one type of message signal, the attribute $X(E)$ can be replaced by a list $X(E(i))$ for each type $i$ of message presented in the network. For that situation, the conditional line $7$ must be verified for all types of connnections: $\exists \ X \in \bar{T} : | E_k^{-1}(\{w_i\})\cap S | = X(E(k))$.

@@

\begin{algorithm}[h]
	\SetAlgoLined
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	\Input{A network $G(V, E)$}
	\Output{The minimal fibration partition $\bar{Q}$ of $G(V,E)$}
	%\KwResult{}
	Initialize $S$ as an empty set\;
	Initialize $L$ as an empty queue\;
	Initialize $\bar{P'}$, $\bar{P''}$, $\bar{Q}$ as empty partitions\;
	$\forall w_i \in V \Rightarrow B'_{i} = \{ w_i : |E^{-1}(\{w_i\})|=0 \}$\;
	$\forall v_i \in V \Rightarrow A_i = \{ v_i : E^{-1}(\{v_i\}) = \{v_i\} \}$\;
	$B'' = \{ v \in V : |E^{-1}(\{v\})| \geq 1 \}$\;
	\textit{push} all $B'_{i}$ to $\bar{P'}$\;
	\textit{push} $B''$ to $\bar{P''}$\;
	\textit{enqueue} $B'' \in \bar{P''}$ to $L$\;
	\textit{enqueue} all $A_i$ to $L$\;
	\textit{enqueue} all blocks $B' \in \bar{P'}$ to $L$\;
	$\bar{Q} \leftarrow \bar{P''}$\;
	\While{$|L| \neq 0$}
	{
		$S \leftarrow \text{\textit{dequeue}}(L)$\;
		$\bar{Q} \leftarrow \text{\textit{I-input}}(S, \bar{Q}, L)$
	}
	\caption{Coarsest Refinement Graph Partitioning}
	\label{alg:partitioning}
\end{algorithm}

>>>>

@@

\begin{algorithm}[!t]
	\SetAlgoLined
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	\Input{A network $G(V, E)$}
	\Output{The minimal fibration partition $\bar{Q}$ of $G(V,E)$}
	%\KwResult{}
	Initialize $S$ as an empty set\;
	Initialize $L$ as an empty queue\;
	Initialize $\bar{P'}$, $\bar{P''}$, $\bar{Q}$ as empty partitions\;
	$\forall w_i \in V \Rightarrow B'_{i} = \{ w_i : |E^{-1}(\{w_i\})|=0 \}$\;
	$\forall v_i \in V \Rightarrow A_i = \{ v_i : E^{-1}(\{v_i\}) = \{v_i\} \}$\;
	$B'' = \{ v \in V : |E^{-1}(\{v\})| \geq 1 \}$\;
	\textit{push} all $B'_{i}$ to $\bar{P'}$\;
	\textit{push} $B''$ to $\bar{P''}$\;
	\textit{enqueue} $B'' \in \bar{P''}$ to $L$\;
	\textit{enqueue} all $A_i$ to $L$\;
	\textit{enqueue} all blocks $B' \in \bar{P'}$ to $L$\;
	$\bar{Q} \leftarrow \bar{P''}$\;
	\While{$|L| \neq 0$}
	{
		$S \leftarrow \text{\textit{dequeue}}(L)$\;
		$\bar{Q} \leftarrow \text{\textit{I-input}}(S, \bar{Q}, L)$
	}
	\caption{Coarsest Refinement Graph Partitioning}
	\label{alg:partitioning}
\end{algorithm}

In the algorithm \ref{alg:split}, our \textit{I-split} function receives a set $S$ and the partition $\bar{Q}$ as input and returns a input-tree stable $\bar{Q}$ with respect to $S$ as output. Besides its list of nodes, a block $X$ should have another attribute acessed as $X(E)$, which receives, during the splitting process, the number of inward links coming from the current refinement set $S$. This way, a node $w$ belonging to the block splitted can be put in the block $X \in \bar{T}$ that has the same attribute value, like stated in the conditional expression at line $7$ of the algorithm \ref{alg:split}. In cases where the type of connections are non-trivial, i. e., there is more than one type of message signal, the attribute $X(E)$ can be replaced by a list $X(E(i))$ for each type $i$ of message presented in the network. For that situation, the conditional line $7$ must be verified for all types of connnections: $\exists \ X \in \bar{T} : | E_k^{-1}(\{w_i\})\cap S | = X(E(k))$.

@@

\subsection{Branching ratio determination}

After the proper identification of the fibers over the network, we should classify each fiber according to two fundamental values: the fundamental class number $n$ and the subclass number $\ell$. The subclass value is easily obtained, since it represents the number of external nodes that directly regulates the fiber. The fundamental class, however, may be no so straightforward to calculate if one chooses an eigenvalue decomposition algorithm of the adjacency matrix $\mathbf{A}$ characteristic of the network. The value of $n$  is directly related to cycles of information in the network, quantifying the loops of the fibers. At the same time, $n$ is also the branching ratio of the fiber input-tree, where the ratio is defined by the number of nodes $a_{j+1}$ belonging to a given height level $j+1$ of the input-tree and the number of nodes $a_j$ at the below height $j$ for large enough $j \rightarrow \infty$. This way, the branching ratio is defined as
\begin{equation}
	n = \lim _{j \rightarrow \infty}\bigg(\dfrac{a_{j+1}}{a_j}\bigg)
\end{equation}
where $n$ can be either an integer branching ratio or a golden fibonacci ratio resulted by longer loop pathways with size $d \geq 2$.

Concerning that, here I propose an efficient and simple method to calculate the value of $n$ by counting the number of nodes in each height level of the input-tree of a given node. For infinite input-trees, \textit{i. e.}, for fibers with loops, the algorithm performs the calculation in each tree level until a determined precision is reached, defined by a small value $\delta < 1$. The aim of the algorithm is, for each step, build two following layers of the input-tree in order to calculate directly the value of $n$ by counting the number of nodes $a_j$ and $a_{j+1}$ presented in each of these layers. We define $n_j$ as the ratio $\frac{a_{j+1}}{a_j}$. The algorithm will stop when $|n_j - n_{j-1}| < \delta$.

The implementation of the algorithm is quite simple, making use of only one type of data structures: stacks. The algorithm consists of two steps, the first one being the verification of the existence of loops on the input-tree, from which only if this verification is true we go to the second step. The existence of loops in the input-tree implies an infinite tree. After that, starting from the root node $v$ of the input-tree, we find its nearest incoming neighbors $E^{-1}(\{v\})$ and store them in a first stack $S_1$, representing this way the first layer of the input-tree, from which we can obtain the value of its size $a_1$. Next, we pop each element of $S_1$ and get their incoming neighbors $E^{-1}(\{pop(S_1)\})$ and store them in $S_2$ until $S_1$ is empty. Then, $S_2$ will store the second layer of the input-tree, from which we get its $a_2$, allowing the calculation of $n_2$. Since at this time $S_1$ is empty, we get the incoming neighbors of each element of $S_2$ and stores in $S_1$, and this process is repeated, exchanging $S_1$ e $S_2$ as incoming neighbors supplier and deposit. This way, we can calculate indefinetely the values of $n_j$ until the precision is good enough. Of course, the precision $\delta$ will be only useful for fibonacci fibers, since integer branching ratio fibers will satisfy the precision right way, since $n_3 = n_2$ for these fibers. The algorithm pseudocode implementation is given in \ref{alg:branchratio}.

\begin{algorithm}[!b]
	\SetAlgoLined
	\SetKwInOut{Input}{Input}
    \SetKwInOut{Output}{Output}
	\Input{A node $v \in V$ for a network $G(V, E)$}
    \Output{$n$ representing the branching ratio of the node $v$ input-tree}
    Initialize $\mathbf{s_1}$ and $\mathbf{s_2}$ as empty stacks\;
	Initialize $\mathbf{Sup}$, $\mathbf{Depot}$ and $\mathbf{Aux}$ as stack pointers\;
	\eIf{\text{checkloop(v)} $=$ TRUE}
	{
		$n_j, n_{j+1} \leftarrow 0.0$\;
		push($\mathbf{s_1}$, v)\;
		$\mathbf{Sup} \leftarrow \mathbf{s_1}$\;
		$\mathbf{Depot}$ $\leftarrow$ $\mathbf{s_2}$\;
		\While{$| n_{j+1} - n_j | > \delta$ \textbf{or} $n_{j+1} = 0$ }
		{
			$a_j \leftarrow |\mathbf{Sup}|$\;
			$n_j \leftarrow n_{j+1}$\;
			\While{ $|\mathbf{Sup}| \neq 0$}
			{
				$u \leftarrow $ pop($\mathbf{Sup}$)\;
				$\forall w \in E^{-1}(\{u\}) \Rightarrow$ push($\mathbf{Depot}$, $w$)\;
			}
			$a_{j+1} \leftarrow |\mathbf{Depot}|$\;
			$n_{j+1} \leftarrow \bigg(\dfrac{a_{j+1}}{a_j}\bigg)$\;
			$\mathbf{Aux} \leftarrow \mathbf{Depot}$\;
			$\mathbf{Depot} \leftarrow \mathbf{Sup}$\;
			$\mathbf{Sup} \leftarrow \mathbf{Aux}$\;
		}
	}
	{
		$n_{j+1} \leftarrow 0$\;
	}
	$n \leftarrow n_{j+1}$\;
	\caption{Input-tree branching ratio determination}
	\label{alg:branchratio}
\end{algorithm}

The checkloop($v$) function can be easily implemented through a Depth-First Search or Breadth-First Search algorithm for the node $v$ to find its strongly connected component. This means that starting from the root node $v$, the algorithm traverse only the neighbors that points to the current node. Therefore, the algorithm presented above has a linear runtime complexity with the size of the tree. Its worst-case scenario is modulated by the $\delta$ precision factor only for fibonacci fibers, since these fibers are represented by fractal $n = \phi_d$ values, where $d$ is the size of the information cycle.
